{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-08 documents/brillouin_pulse_math.tex
scan converter, but fucking why

@@

The change in loss (the complex part of the permittivity, or the) and increase in penetration depth 
-

>>>>

Such thin

@@

The change in loss (the complex part of the permittivity, or the) and increase in penetration depth

While it is clearly possible to produce this abnormal penetration (any sharp edge suffices), it was not obvious to us that a waveform 
could be constructed that would be 
an effective driver for the normal modes in question. Oughston ; if the pulses are too close together, they distort the precursor thus 
formed.

### 2021-01-08 documents/fluorescence.tex
VMD signal library
scan converter, but fucking why

>>>>

Fluoris

 LOL

(apologies to Floris Laporte)

sketches of light source in inkscape

from [], using ImageJ to stack. works great on cheap cmos cameras - interestingly doesn't work at all on more expensive cameras. - 
almost good enough - great for diagnostics

interestingly, the fact that the camera has color is quite valuable; filtering the green out can increase sensitivity a lot

a 30-s exposure on a cheap camera also almost got there.
